Trends of SDR in Thessaloniki 

### 2022-10-09 Article.Rmd
Commit 2022-10-09 20:17

output:
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              yes
    fig_width:        7
    fig_height:       4.5
  html_document:
    toc:        true
    fig_width:  7.5
    fig_height: 5
date: "`r format(Sys.time(), '%F')`"

@@

<!-- screening -->
All measurements have been manually screened for inconsistencies and obviously 
problematic data have been excluded.
<!-- physical quantities -->
The conversions to irradiance was done using the calibration factor
.......chp1.... cmp21......
, and adjusting for the dark signal offset daily, using the nights 
before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied adjusted for the site,
based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006]. 
Only data characterized with low quality indicators was rejected.
<!-- Data preparation -->
Due to the large measurement uncertainty near the horizon we exclude
all measurements with SZA greater than $85^\circ$. Moreover, due to 
nearby hills and buildings we remove data with azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$, as at 
those cases the Sun can not viewed by the instruments.

@@

<!-- Clear Sky -->
We will use two dataset of our measurements, one for all sky conditions (ALL),
which is the whole available data, and one filtered for 'clear sky' 
conditions (CS). The latter was created, using a method adapted to our 
site as proposed by @Long2000 and by @Reno2016.

@@

Both dataset were aggregate in SZA bins by am, pm, am+pm

@@

@@

Deseasonlized

## Longterm trends

>>>>

output:
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
  html_document:
    toc:        true
    fig_width:  7.5
    fig_height: 5
date: "`r format(Sys.time(), '%F')`"

@@

<!-- screening -->
All measurements have been manually screened for inconsistencies and obviously 
problematic data have been excluded.
<!-- physical quantities -->
The conversions to irradiance was done using the available calibrations factors,
for both instruments. For CHP1........
.......chp1.... cmp21......
, and adjusting for the dark signal offset daily, using the nights 
before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied adjusted for the site,
based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006]. 
Only data characterized with low quality indicators was rejected.
<!-- Data preparation -->
Due to the large measurement uncertainty near the horizon we exclude
all measurements with SZA greater than $85^\circ$. Moreover, due to 
nearby hills and buildings we remove data with azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$, as at 
those cases the Sun was not visible by the instruments.

@@

<!-- Clear Sky -->
We using two selection of our measurements dataset, one with all sky conditions (ALL),
consisting of the whole available data, and one filtered for 'clear sky' 
conditions (CS). The latter was created, using a method adapted to our 
site, and was proposed by @Long2000 and by @Reno2016.

@@

Both dataset were aggregate in $1^\circ$ SZA bins by am, pm, am+pm

some data was rejected.......

@@

daily sum

@@

<!-- Deseasonalization -->
We remove the natural occurring seasonal variation, by calculating the mean
values for the corresponding time step, and subtracting them .........

## Long-term trends
